Defending Against Web Application Attacks: Approaches, Challenges and Implications \newline\newline \small{\textbf{Response to Review Comments}}

### 2016-09-17 docs/comments/comments.tex
updated the "response to reviewers" doc per Panos comments

\noindent
{\bf Response:}
In general,
a way to check if a mechanism can be examined
based on our criteria,
is to see if and how it fits into our
exploitation model (point of detection).
Specifically,
application firewalls
fit into our study.
Besides,
in reference~\cite{DPJV06}
the authors indicate three mechanisms~\cite{BK04,PB05,HO05b}
that we include in our analysis as
application firewalls.\\

@@

\noindent
{\bf Response:}
This is a valid comment.
However,
in order to avoid penalizing recent research,
we have also included recent papers
even though they have been cited less than twenty times.

@@

\noindent
{\bf Response:}
In our study,
we observed that there are cases where
mechanisms coming from the same category
can be bypassed by similar attack patterns.
This denotes that there are issues
found in the design of each approach.
We also observed that mechanisms which
combine characteristics
from different categories,
could deal with these threats.
This indicates that when solutions
borrow elements from other categories
they could become more effective.
Mechanisms can also work together
to defend against different attacks.
For instance,
developers could employ both {\sc csp}
and \textsc{sql}rand
to deal with {\sc xss} and
{\sc sql} injection respectively.
We have updated Subsection 7.3
(now named ``Performance Overhead,
Deployment and Security Remarks")
to include all the above remarks.\\

>>>>

\noindent
{\bf Response:}
In general,
a way to check if a mechanism can be examined
based on our criteria,
is to see if and how it fits into our
exploitation model (point of detection).
Specifically,
application firewalls
fit into our study.
Indeed,
in reference~\cite{DPJV06}
the authors indicate three mechanisms~\cite{BK04,PB05,HO05b}
that we include in our analysis as
application firewalls.\\

@@

\noindent
{\bf Response:}
This is a valid comment.
Indeed,
in order to avoid penalizing recent research,
we have also included recent papers
even though they have been cited less than twenty times.

@@

\noindent
{\bf Response:}
In our study,
we observed that there are cases where
mechanisms coming from the same category
can be bypassed by similar attack patterns.
This denotes that there are issues
found in the design of each approach.
We also observed that mechanisms that
combine characteristics
from different categories
could deal with these threats.
This indicates that when solutions
borrow elements from other categories
they could become more effective.
Mechanisms can also work together
to defend against different attacks.
For instance,
developers could employ both {\sc csp}
and \textsc{sql}rand
to deal with {\sc xss} and
{\sc sql} injection respectively.
We have updated Subsection 7.3
(now named ``Performance Overhead,
Deployment and Security Remarks")
to include all the above remarks.\\
